
\DeclareUnicodeCharacter{00A0}{ }
\usepackage[utf8x]{inputenc}
---
title: "Final Project - EDA"
author: "Keerthi Sreenivas Konjety, Vishnu Elangonvan"
date: "12/15/2021"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
mkt = read.csv("marketing_campaign.csv")
```

Abstract of my EDA Analysis:

1.Data Cleaning
2.Univariate Analysis - Questions Answered:
   ### 1.Which aged customers purchase highly?
   ### 2.Among all the products that we sell, which one is highly influenced by most of our customers?
   ### 3.How is the performance of the campaigns?
3.Bivariate Analysis - Questions Answered:
      ### Income and Expense variation based on Marital Status
      ### Education vs Category of Expenses
   

```{r}
library(skimr)
library(dplyr)
library(DataExplorer)
library(plotly)
library(ggplot2)
library(IRdisplay)
mkt = read.csv("marketing_campaign.csv")

mkt_df=data.frame(mkt)
copy_df = data.frame(mkt_df)

```


```{r}
plot_intro(mkt_df,title='Mkt dataset')
```
Data Exploration function from plot_intro gives me the above results.

```{r}
head(mkt_df,5)
```
This gives me the first five rows of my data.


```{r}
skim(mkt_df)
```
### Observations!

At the Initial observation
- There are 2240 entries and 29 columns
- In columns 'z_costcontact','z_revenue' all values are equal, we will drop this columns from the mkt.
- No duplicated values and errors (at the first glance)
- Only 'Income' column has missing values



```{r}
#Filling the missing value with median value
mkt_df$Income[is.na(mkt_df$Income)]=median(mkt_df$Income,na.rm=T)
#Counting the missing value in Income column
sum(is.na(mkt_df$Income))
```


```{r}
#Finding the no of unique values in each column
sapply(mkt_df, function(x) length(unique(x)))
#Since the columns z_costcontact and z_revenue has one unique value, we will remove those columns
#Removing the unwanted columns
mkt_df=subset(mkt_df,select=-c(Z_CostContact,Z_Revenue))
```

```{r}
#Old dimension of main_df is 2240 29
dim(mkt_df)
```


### Univariate Analysis Qn 1-3




### 1.Which aged customers purchase highly?
```{r}
current_date= Sys.Date()
current_year = format(current_date,format="%Y")
current_year = as.integer(current_year)
Age= c(current_year - mkt_df$Year_Birth)
#Adding Age column to main_df dataframe
mkt_df['Age']=Age
#Calculating maximum age of customers
max(mkt_df$Age)
#Calculating minimum age of customers
min(mkt_df$Age)
#Calculating average for age of customers
```
Calculating maximum age of customers is 128
Calculating minimum age of customers is 25

```{r}
children = mkt_df %>% filter(Age < 15) %>% summarize(n())
young = mkt_df %>% filter(15 <= Age & Age <= 25) %>% summarize(n())
middle_aged = mkt_df %>% filter(25 < Age & Age <= 59) %>% summarize(n())
old  = mkt_df %>% filter( 60 <= Age & Age <=128 ) %>% summarize(n())


children = as.integer(children)
young = as.integer(young)
middle_aged = as.integer(middle_aged)
old = as.integer(old)

count = c(children,young,middle_aged,old)
labels_age = c('Children','Young','Middle Aged','Old')

children#No of Children
young#No of Children
middle_aged#No of Children
old#No of Children
```
### Observations!
- 70% of customers in the data are middle aged
- Only 29% of customers in the date are old
- There is no significant amount of children and young customers
### 2.Among all the products that we sell, which one is highly influenced by most of our customers?
```{r}
# Combining different dataframe into a single column to reduce the number of dimension

mkt_df['Expenses'] = mkt_df['MntWines'] + mkt_df['MntFruits'] + mkt_df['MntMeatProducts'] + 
mkt_df['MntFishProducts'] + mkt_df['MntSweetProducts'] + mkt_df['MntGoldProds']

#Maximum Expenses
max(mkt_df$Expenses)
#Minimum Expenses
min(mkt_df$Expenses)
#Average Expenses
mean(mkt_df$Expenses)
```

```{r}
TotalExpense = sum(mkt_df$Expenses)
percent_w = (sum(mkt_df$MntWines)/TotalExpense)*100
percent_f = (sum(mkt_df$MntFruits)/TotalExpense)*100
percent_mp = (sum(mkt_df$MntMeatProducts)/TotalExpense)*100
percent_fp = (sum(mkt_df$MntFishProducts)/TotalExpense)*100
percent_sp = (sum(mkt_df$MntSweetProducts)/TotalExpense)*100
percent_gp = (sum(mkt_df$MntGoldProds)/TotalExpense)*100


percent_w
percent_f
percent_mp
percent_fp
percent_sp
percent_gp

per_ex = c(percent_w,percent_f,percent_mp,percent_fp,percent_sp,percent_gp)
labels_ex = c('MntWines','MntFruits','MntMeatProducts','MntFishProducts','MntSweetProducts','MntGoldProducts')
```
Percent_Wine is 50.17
Percent_Fruits is 4.34
Percent_MeatProducts is 27.55
Percent_FishProducts is 6.19
Percent_SweetProducts is 4.46
Percent_GoldProducts  is 7.26

As we can see, people tend to spend more on wine products comparing to the rest of the products.





### 3.How is the performance of the campaigns?
```{r}
#Finding unique values in AcceptedCmp1 column
unique(mkt_df$AcceptedCmp1)
##Same unique values for other AcceptedCmp variables


# Combining different dataframe into a single column to reduce the number of dimension

mkt_df['TotalAcceptedCmp'] = mkt_df['AcceptedCmp1'] + mkt_df['AcceptedCmp2'] + mkt_df['AcceptedCmp3'] + 
mkt_df['AcceptedCmp4'] + mkt_df['AcceptedCmp5']
```




```{r}
#Creating table for TotalAcceptedCmp column

table_ac = table(mkt_df$TotalAcceptedCmp)
per_ac = as.vector(prop.table(table_ac)*100)
labels_ac = c('0','1','2','3','4')
df_ac = data.frame(labels_ac,per_ac)
df_ac
```

```{r}
#Calculating percentage for each of the category in TotalAcceptedcmp column

TotalAcceptedOffers = sum(mkt_df$TotalAcceptedCmp)
percent_c1 = (sum(mkt_df$AcceptedCmp1)/TotalAcceptedOffers)*100
percent_c2 = (sum(mkt_df$AcceptedCmp2)/TotalAcceptedOffers)*100
percent_c3 = (sum(mkt_df$AcceptedCmp3)/TotalAcceptedOffers)*100
percent_c4 = (sum(mkt_df$AcceptedCmp4)/TotalAcceptedOffers)*100
percent_c5 = (sum(mkt_df$AcceptedCmp5)/TotalAcceptedOffers)*100

per_cmp = c(percent_c1,percent_c2,percent_c3,percent_c4,percent_c5)
labels_cmp = c('Campaign 1','Campaign 2','Campaign 3','Campaign 4','Campaign 5')
```
### Observations!

- 79.33% of Customers accepted no offers in the campaigns 
- 14.50% of Customers accepted only one offer in the campaigns 
- 3.70% of Customers accepted two offer in the campaigns 
- 1.96% of Customers accepted three offer in the campaigns
- 0.49% of Customers accepted four offer in the campaigns

### Insights
1.Moreover, we observe that we don't have any customers who accepted all the five offers in the campaigns organized.
2.Having a high percentage about acceptance of no offers in the campaigns conducted shows that have to significantly improve the performance in the campaigns.
3.Most customers accepted the offers in the campaign 4 but only small amount of customers have accepted the offers in the 2nd campaign








### Bivariate Analysis

```{r}
#Creating a table for Education variable
table_ed = sort(table(mkt_df$Education),decreasing=T)
per_ed = as.vector((prop.table(table_ed)*100))
labels_ed = c('Graduation','PhD','Master','2n Cycle','Basic')
df_ed = data.frame(labels_ed,per_ed)
df_ed
#Creating a table for Education variable
table_ms = sort(table(mkt_df$Marital_Status),decreasing=T)
per_ms = as.vector(prop.table(table_ms)*100)
labels_ms = c('Married','Together','Single','Divorced','Widow','Alone','Absurd','YOLO')
df_ms = data.frame(labels_ms,per_ms)
df_ms

```
### 1.Income and Expense variation based on Marital Status
```{r}

#Filtering the dataframe based on the categories of Marital Status column

married = mkt_df %>% filter(Marital_Status == 'Married') %>% select(Income, Expenses)
avg_married_ic = mean(married$Income)
avg_married_ex = mean(married$Expenses)

together = mkt_df %>% filter(Marital_Status == 'Together') %>% select(Income, Expenses)
avg_together_ic = mean(together$Income)
avg_together_ex = mean(together$Expenses)

single = mkt_df %>% filter(Marital_Status == 'Single') %>% select(Income, Expenses)
avg_single_ic = mean(single$Income)
avg_single_ex = mean(single$Expenses)

divorced = mkt_df %>% filter(Marital_Status == 'Divorced') %>% select(Income, Expenses)
avg_divorced_ic = mean(divorced$Income)
avg_divorced_ex = mean(divorced$Expenses)

widow = mkt_df %>% filter(Marital_Status == 'Widow') %>% select(Income, Expenses)
avg_widow_ic = mean(widow$Income)
avg_widow_ex = mean(widow$Expenses)

alone = mkt_df %>% filter(Marital_Status == 'Alone') %>% select(Income, Expenses)
avg_alone_ic = mean(alone$Income)
avg_alone_ex = mean(alone$Expenses)

absurd = mkt_df %>% filter(Marital_Status == 'Absurd') %>% select(Income, Expenses)
avg_absurd_ic = mean(absurd$Income)
avg_absurd_ex = mean(absurd$Expenses)

yolo = mkt_df %>% filter(Marital_Status == 'YOLO') %>% select(Income, Expenses)
avg_yolo_ic = mean(yolo$Income)
avg_yolo_ex = mean(yolo$Expenses)

avg_ms_ic=c(avg_married_ic,avg_together_ic ,avg_single_ic, avg_divorced_ic ,avg_widow_ic,avg_alone_ic,avg_absurd_ic
,avg_yolo_ic)
avg_ms_ex=c(avg_married_ex,avg_together_ex ,avg_single_ex, avg_divorced_ex ,avg_widow_ex,avg_alone_ex,avg_absurd_ex
,avg_yolo_ex)
df_ms_ic_ex = data.frame(labels_ms,avg_ms_ic,avg_ms_ex)
df_ms_ic_ex

```
avg_ms_ic (Income Variable)
avg_ms_ex (Expenses)

### Observations!
- Customers with the marital status 'Absurd' has high income and they spend highly than the other customers.Looks like an Outlier though
- Customers who are alone, have low income and spendings. 
The reason might be these type of customers are too old or too young so that they cannot earn lot of money




### 2.Education vs Category of Expenses

```{r}
#Filtering the dataframe based on the categories of Education column

graduation = mkt_df %>% filter(Education == 'Graduation') %>% select(MntWines,MntFruits, MntMeatProducts,MntSweetProducts,MntFishProducts,MntGoldProds)
avg_graduation_mw = mean(graduation$MntWines)
avg_graduation_mf = mean(graduation$MntFruits)
avg_graduation_mp = mean(graduation$MntMeatProducts)
avg_graduation_fp = mean(graduation$MntFishProducts)
avg_graduation_sp = mean(graduation$MntSweetProducts)
avg_graduation_gp = mean(graduation$MntGoldProds)

phd = mkt_df %>% filter(Education == 'PhD') %>% select(MntWines,MntFruits, MntMeatProducts,MntSweetProducts,MntFishProducts,MntGoldProds)
avg_phd_mw = mean(phd$MntWines)
avg_phd_mf = mean(phd$MntFruits)
avg_phd_mp = mean(phd$MntMeatProducts)
avg_phd_fp = mean(phd$MntFishProducts)
avg_phd_sp = mean(phd$MntSweetProducts)
avg_phd_gp = mean(phd$MntGoldProds)


master = mkt_df %>% filter(Education == 'Master') %>% select(MntWines,MntFruits, MntMeatProducts,MntSweetProducts,MntFishProducts,MntGoldProds)
avg_master_mw = mean(master$MntWines)
avg_master_mf = mean(master$MntFruits)
avg_master_mp = mean(master$MntMeatProducts)
avg_master_fp = mean(master$MntFishProducts)
avg_master_sp = mean(master$MntSweetProducts)
avg_master_gp = mean(master$MntGoldProds)

second_cycle = mkt_df %>% filter(Education == '2n Cycle') %>% select(MntWines,MntFruits, MntMeatProducts,MntSweetProducts,MntFishProducts,MntGoldProds)
avg_second_cycle_mw = mean(second_cycle$MntWines)
avg_second_cycle_mf = mean(second_cycle$MntFruits)
avg_second_cycle_mp = mean(second_cycle$MntMeatProducts)
avg_second_cycle_fp = mean(second_cycle$MntFishProducts)
avg_second_cycle_sp = mean(second_cycle$MntSweetProducts)
avg_second_cycle_gp = mean(second_cycle$MntGoldProds)

basic = mkt_df %>% filter(Education == 'Basic') %>% select(MntWines,MntFruits, MntMeatProducts,MntSweetProducts,MntFishProducts,MntGoldProds)
avg_basic_mw = mean(basic$MntWines)
avg_basic_mf = mean(basic$MntFruits)
avg_basic_mp = mean(basic$MntMeatProducts)
avg_basic_fp = mean(basic$MntFishProducts)
avg_basic_sp = mean(basic$MntSweetProducts)
avg_basic_gp = mean(basic$MntGoldProds)

avg_ed_mw=c(avg_graduation_mw,avg_phd_mw ,avg_master_mw, avg_second_cycle_mw ,avg_basic_mw)
avg_ed_mf=c(avg_graduation_mf,avg_phd_mf,avg_master_mf, avg_second_cycle_mf ,avg_basic_mf)
avg_ed_mp=c(avg_graduation_mp,avg_phd_mp ,avg_master_mp, avg_second_cycle_mp ,avg_basic_mp)
avg_ed_fp=c(avg_graduation_fp,avg_phd_fp ,avg_master_fp, avg_second_cycle_fp ,avg_basic_fp)
avg_ed_sp=c(avg_graduation_sp,avg_phd_sp ,avg_master_sp, avg_second_cycle_sp ,avg_basic_sp)
avg_ed_gp=c(avg_graduation_gp,avg_phd_gp ,avg_master_gp, avg_second_cycle_gp ,avg_basic_gp)
df_ed_prods = data.frame(labels_ed,avg_ed_mw,avg_ed_mf,avg_ed_mp,avg_ed_fp,avg_ed_sp,avg_ed_gp)
df_ed_prods
```
### Observations!
avg_ed_mw Wines
avg_ed_mf Fruits
avg_ed_mp MeatProducts
avg_ed_fp FishProducts
avg_ed_sp SweetProducts
avg_ed_gp GoldProds
- Customers with a PhD degree tend to buy wine products largely than the other educated customers
- Except the products wine and meat, customers tend to spend very little amount on all the other products
- Customers with a basic education tend to spend very little amount to buy the products
